Favourable Conservation Status (FCS): <br> Analysis of Bauer et al. (unpublished) Field experiment

### 2022-11-18 R/model_fcs_markdown.Rmd
Update

@@

```{r}
iter = 10000
chains = 4
thin = 2
seed = 123
priors <- c(
  set_prior("normal(0, 1)", class = "b"),
  set_prior("normal(0.1, 1)", class = "b", coef = "sand_ratio25"),
  set_prior("normal(0.2, 1)", class = "b", coef = "sand_ratio50"),
  set_prior("normal(0.1, 1)", class = "b", coef = "expositionsouth"),
  set_prior("normal(0.1, 1)", class = "b", coef = "survey_year_fct2019"),
  set_prior("normal(0.2, 1)", class = "b", coef = "survey_year_fct2020"),
  set_prior("normal(0.3, 1)", class = "b",coef = "survey_year_fct2021"),
  set_prior("cauchy(0, 1)", class = "sigma")
)
```

>>>>

Possible prior distributions

```{r}
ggplot(data = data.frame(x = c(-1, 1)), aes(x = x)) +
  stat_function(fun = dnorm, n = 101, args = list(mean = 0.1, sd = 1)) +
  expand_limits(y = 0) + ggtitle("Normal distribution")
ggplot(data = data.frame(x = c(-1, 1)), aes(x = x)) +
  stat_function(fun = dcauchy, n = 101, args = list(location = 0, scale = 1)) +
  expand_limits(y = 0) + ggtitle("Cauchy distribution")
ggplot(data.frame(x = c(-1, 1)), aes(x = x)) +
  stat_function(fun = dstudent_t, args = list(df = 3, mu = 0, sigma = 2.5)) +
  expand_limits(y = 0) + ggtitle(expression(Student ~ italic(t)"-distribution"))
```

@@

```{r}
iter = 10000
chains = 4
thin = 2
seed = 123
warmup = floor(iter / 2)
priors <- c(
  set_prior("normal(0, 1)", class = "b"),
  set_prior("normal(0.1, 1)", class = "b", coef = "sand_ratio25"),
  set_prior("normal(0.2, 1)", class = "b", coef = "sand_ratio50"),
  set_prior("normal(0.1, 1)", class = "b", coef = "survey_year_fct2019"),
  set_prior("normal(0.2, 1)", class = "b", coef = "survey_year_fct2020"),
  set_prior("normal(0.3, 1)", class = "b",coef = "survey_year_fct2021"),
  set_prior("cauchy(0, 1)", class = "sigma")
)
```
